\documentclass[a4paper,10pt]{article}
\usepackage[onehalfspacing]{setspace}
\hoffset=-1.0cm\voffset=-2.0cm \textwidth=155mm\textheight=220mm

\usepackage{authblk}

\title{Causality Inference in a nonstationary and nonhomogenous framework}
\author[a]{Illia Horenko}
\author[a]{\underline{Patrick Gagliardini}}
\author[b]{William Sawyer}
\author[a]{\underline{Luk\'{a}\v{s} Posp\'{i}\v{s}il}}
\affil[a]{Universit\`{a} Svizzera Italiana, Lugano, Switzerland}
\affil[b]{Swiss National Supercomputing Centre (CSCS/ETH Zurich), Switzerland}
\affil[ ]{\textit {\{illia.horenko,patrick.gagliardini,lukas.pospisil\}@usi.ch, william.sawyer@cscs.ch}}

\date{}

\begin{document}
\pagenumbering{gobble}
  \maketitle



\par
\vspace{4mm}

\noindent
The project deploys these statistical and computational techniques to develop a novel approach to causality inference 
in multivariate time series of economical data on equity and credit risks. The methods build on recent research of project participants, \cite{bib:HorenkoGerber}. They improve on classical approaches to causality analysis such as Granger causality (see \cite{bib:Granger})  by accommodating 
general forms of nonstationarity and non-homogeneity. 
We are interested in clustering of time series based on a minimization of the averaged clustering
functional, which describes the mean distance between observation data
and its representation in terms of given number of abstract models of a certain predefined class.
We are using finite element framework to the problem of time series analysis and to propose a numerical scheme
for time series clustering \cite{bib:horenko}. \newline
One of the most challenging component of the numerical solution is 
Quadratic Programming (QP) problem with the combination of linear equality and bound inequality constraints.
In our contribution, we compare tree different QP algorithms to solve this problem -
Augmented Lagrangian method combined with active-set strategy \cite{bib:DosPos}, Interior-point methods \cite{bib:Boyd} and
the modification of Spectral Projected Gradient method for QP \cite{bib:spg}, \cite{bib:Pos}.
We demonstrate and compare the efficiency of the methods solving practical benchmarks. \newline





%% BIBLIOGRAPHY 
\begin{thebibliography}{}

\bibitem{bib:horenko} 
Horenko I.:
{\em Finite element approach to clustering of multidimensional time series}.
SIAM Journal of Scientific Computing 32, pp. 62--83, (2010).

\bibitem{bib:HorenkoGerber}
Horenko I., and Gerber S.:
{\em On inference of causality for discrete state models in a multiscale context}.
Proc. Natl. Acad. Sci. USA (PNAS), DOI: 10.1073/pnas.1410404111, (2014).

\bibitem{bib:spg} 
  Birgin E.G., Mart\'{i}nez J.M., and Raydan M.:
  {\em Nonmonotone spectral projected gradient methods on convex sets}.
  SIAM Journal on Optimization 10, pp. 1196--1211, (2000).

\bibitem{bib:Boyd}
  Boyd S., Vandenberghe L.:
  {\em Convex Optimization}. 
  Cambridge University Press, New York, 1st edition, (2004).

\bibitem{bib:DosPos}
 Dost\'{a}l Z., Posp\'{i}\v{s}il L.:
 {\em Optimal iterative QP and QPQC algorithms}.
 Annals of Operations Research, DOI: 10.1007/s10479-013-1479-0, (2013).  

\bibitem{bib:Granger}
Granger C.:
{\em Investigating Causal Relations by Econometric Models and Cross-Spectral methods}.
Econometrica, 37, pp. 424--438, (1969).


\bibitem{bib:Pos}
 Posp\'{i}\v{s}il L.:
 {\em Development of Algorithms for Solving Minimizing Problems with Convex Quadratic Function on Special Convex Sets and Applications}.
 PhD Thesis, V\v{S}B-TU Ostrava, (2015).


  

   
\end{thebibliography}


\end{document}
